%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventryroles}

%---------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Lead Software Engineer}
    {Capital One}
    {Chicago, IL}
    {Feb. 2025 - Present}
    {
      \begin{cvitems}
        \item {Lead and mentored a team of junior engineers, fostering technical growth and collaboration}
        \item {Enabled adoption of new AWS services by collaborating with internal and external teams}
        \item {Partnered with AWS engineers to pilot and integrate new cloud features}
        \item {Resolved critical security issues in a highly regulated environment}
        \item {Enhanced Jenkins pipelines, reducing developer build times}
        \item {Provided on-call support, ensuring rapid resolution of enterprise-scale incidents}
      \end{cvitems}
    }
\end{cventries}
  
  \cventryroles
    {Member of Technical Staff - 3 (Jan. 2022 - Jan. 2025)}
    {Member of Technical Staff - 2 (Jan. 2020 - Jan. 2022)}
    {VMware} % Organization
    {Austin, TX} % Location
    {Jan. 2020 - Present}
    {
      \begin{cvitems}
        \item {Delivered complex front-end features on schedule, improving user experience and product quality}
        \item {Rearchitected a core service, reducing cloud costs by over \$100k per month}
        \item {Ensured PCI compliance by collaborating with stakeholders and Principal Engineers}
        \item {Introduced telemetry and leveraged data analysis to guide product development}
        \item {Remediated client issues for major financial and federal customers as part of on-call rotation}
        \item {Developed and maintained CI/CD pipelines using Concourse, Jenkins, and custom tools}
        \item {Automated developer workflows, including Change Management and CVE remediation}
        \item {Mentored new team members during transition to full-stack development}
        \item {Authored technical documentation and developer guides for new features}
      \end{cvitems}
    }
\end{cventryroles}
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Developer}
    {General Motors}
    {Austin, TX}
    {Aug. 2014 - Dec. 2019}
    {
      \begin{cvitems}
        \item {Led modernization and standardization of applications using GM's private cloud}
        \item {Evaluated emerging technologies, developed proofs of concept, and presented findings to leadership}
        \item {Deployed and integrated major business applications with existing systems}
        \item {Designed and implemented data ingestion processes for Hadoop platforms}
        \item {Automated manual processes, saving hundreds of operational hours}
        \item {Led a team to deliver file transfer solutions for the Finance vertical}
        \item {Resolved high-priority production incidents, minimizing impact on month-end reporting}
        \item {Collaborated on high-visibility data integration projects within large teams}
      \end{cvitems}
    }
% %---------------------------------------------------------
%   \cventry
%     {TCC Tech Consultant}
%     {University IT Services}
%     {Bloomington, IN}
%     {Aug. 2013 - Aug. 2014}
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Provided direct technical support to students and faculty}
%         \item {Sharpened troubleshooting skills on a wide variety of hardware and software}
%       \end{cvitems}
%     }

\end{cventries}
